---
title: "Objective Function"
output: 
  html_document:
    include:
      in_header: "html/header.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r makecondition, echo=F}
library(reticulate)
use_condaenv("r-reticulate")

library(econR) # 經濟模型程式設計專題用
```


```{r, eval=T, echo=F}
teachDS::img_centering("https://media.giphy.com/media/l2Je1m4g9QMiOsJlS/giphy.gif")
klippy::klippy(lang=c("r","python"))
```


$$\bf{X}\in\mathcal{R}^n\stackrel{f}{\rightarrow}\mathcal{R}^1$$

  * Start from $\bf{X}$, alway the way to $\mathcal{R}^1$.
  
## Let's describe X

```{r}
teachDS::generate_targetPill("Choose a proper type to store X values.")
```

Options:

  * Numeric
  
  * Boolean
  
  * Character
  
  * List

<div class="question">
What is a good type for each agent? 
</div>

```{r}
a <- 3
```

```{python}
a = 3
```


### Consumer


  * 3 apple, 2 bananas

How would you store this information?

### Firm

A coffee shop

  * Input: 200 pounds of coffee beans, 100 liters of water, 3 employees, a shop space of 10 square feet.

### Government

Monitor economic performance closely. 

  * Inflation rates in the past 2 years: 0.25%, 1%
  
  * Unemployment rates in the past 2 years: 4%, 8%
  
  * Real wage growth rates in the past 2 years: 0.1%, 0.8%
  
## Let's image how they care

  * Ordinal? 
  Agents only care at the ranking level. No need to go into detail numeric value assignment.
  
  * Cardinal? 
  Agents cares about the detailed numbers.
