---
title: "Consumer"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
```

<!--
## Consumer
-->

### Utility function

$$U(\bf{X}),$$
where $\bf{X}$ is a vector of commodities. 

```{r}
# Choice of container: numeric vector? list?
X <- ?
```

depends on how do you use $U$ function.

  * $U(c(1,3,4))$ as 3 different commodities.
  
  * $U(c(1,3,4))$ as 1 commodity of 3 quantities.
  
A better way is to use **list** which imposes **structure** so that:
  
  * The **1st** layer differentiate commodities.
  
  * The **2nd** layer shows the quantities of a given commodity.
  
### Consumption bundles

A consumption bundle is **one consumption choice** that can be used to **uniquely** compute consumer's happiness (i.e. utility) gained from consuming that bundle.

```{r}
# 1 commodity with 3 different quantities
list(
  X1=c(1,3,4)
)
# 2 commodities, each with 3 different quantities
list(
  X1=c(1,3,4),
  X2=c(2,3,3)
) -> c23
# 2 commodities, one with 3 different quantities, the other with 1 quantity
list(
  X1=c(1,3,4),
  X2=c(2)
) -> c23_2
```

  * Should **X1, X2** have the same length? 
  
```{r}
as.data.frame(c23) -> c23
as.data.frame(c23_2) -> c23_2 # X2 will be recycled.
```

<div class="alert alert-info">
**list** is a good choice of defining consumption bundde. **as.data.frame** keeps consumption bundles balanced; just be aware of how recycle works in R.
</div>

### Utility mapping

A utility function should be able to map **one bundle** to **one happiness value**

```{r}
bundle_one <- c23[1,]
bundle_two <- c23[2,]
bundle_three <- c23[3,]
```


#### Cobb-Douglas Preference{-}

$$\Pi_{i=1,\dots,n}\bf{X}_i^{\alpha_i},$$
where $\bf{X}_i$ means the quantity of commodity **i** from bundle **X**.

When $n=2$, 

$$\Pi_{i=1,2}\bf{X}_i^{\alpha_i}=\bf{X}_1^{\alpha_1}\bf{X}_2^{\alpha_2}$$
```{r}
X <- bundle_one
```

Consider 
$$\bf{X}_1^{0.3}\bf{X}_2^{1.2}$$

A utility mapping:
$$\mbox{one bundle}\stackrel{\mbox{utility function}}{\longrightarrow}\mathcal{R}^1$$
```{r}
class(bundle_one)
dim(bundle_one)
```
  * one bundle is a data.frame with 1 observation (i.e 1 row)
  
```{r}
cobbDouglass <- function(bundle_one){
  assertthat::assert_that(
    (is.data.frame(bundle_one) &&
      nrow(bundle_one)==1),
    msg="one bundle is a data.frame with 1 observation (i.e 1 row)"
  ) # must have msg=
  util <- bundle_one[[1]]^0.3*bundle_one[[2]]^1.2
  return(util)
}
```


```{r}
cobbDouglass(bundle_one = bundle_one)
```

### Vectorized function (Universal function)

When using function to deliver mapping, functions that deal with multiple argument values (i.e. vector) boost efficiency.

```{r}
# X = c23[1, ]
c23[1,1]**0.3 * c23[1,2]**1.2
# same as
c23[1, ]**c(0.3, 1.2)
prod(c23[1, ]**c(0.3, 1.2))
```

```{r}
c(
  c23[1,1]**0.3, 
  c23[1,2]**1.2
)
```
Same as

```{r}
c23[1, ]**c(
  0.3,
  1.2
)
```

***

```{r}
.Last.value[[1]]*.Last.value[[2]]
```

$\Pi_{i}$ is equivalent to using `prod()`.

```{r}
prod(c23[1,]**c(0.3, 1.2))
```


```{r}
cobbDouglass <- function(one_bundle){
  prod(one_bundle**c(0.3, 1.2))
}
```


***

Is **cobbDouglass** universal?

```{r}
list(
  cobbDouglass_u(c23[1,]),
  cobbDouglass_u(c23[2,]),
  cobbDouglass_u(c23[3,])
)
```

```{r}
cobbDouglass_u(c23)
```


```{r}
purrr::map_dbl(
  1:3,
  ~cobbDouglass(c23[.x,])
)
```

```{r}
cobbDouglass(c23)
```
NOT the same!!! Not UNIVERSAL.

```{r}
c23**c(0.3, 1.2)
```

```{r}
purrr::reduce(
  c23**c(0.3, 1.3), `*`
)
```


```{r}
cobbDouglass_u <- function(bundles){
  purrr::reduce(
    bundles**c(0.3, 1.3), `*`
  )
}
```


```{r}
purrr::map_dbl(
  1:3, 
  ~cobbDouglass_u(c23[.x,]))
# the same as
cobbDouglass_u(c23)
```

