---
title: "Python setup"
output: html_document
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

## Install Python{.tabset}

### Python and Anaconda

Downdown **Python** and package distributor **conda** all at once via:

  * [Anaconda](https://www.anaconda.com/products/individual): Python + conda + other management tools
  
Check your conda info in **Terminal**:  
```
conda info
```

```{r}
list.files("/opt/anaconda3")
```

Update **Anaconda**
```
conda update --prefix /opt/anaconda3 anaconda
```

<div class="alert alert-info">
  * Each version of Python on your system has its own set of packages.  
  * In R, reticulate will automatically find a version of Python that contains the **first package that you import** from R.
</div>

```{r}
install.packages("reticulate")
```

### Conda environment and Python search path

Set RStudio to use your Python binary within a conda environment:
```{r}
library(reticulate)

# create a new environment 
reticulate::conda_create("r-reticulate")
```

Check how Python **binaries**' activating order:
```{r}
reticulate::py_discover_config()
```

## Install Python packages{.tabset}

Install packages in a designated conda environment:

  * via **Conda**
  
  * via **PyPI**
  

### Via Conda

Install via conda distributing system: 
```{r}
reticulate::conda_install("r-reticulate",
                          packages=c("numpy", "pandas"))
```

<div class="alert alert-info">
Only mature packages will be collected to be stored inside conda distribution system. They are stable. However, packages from **individual developer** and the preview version of packages might not be available through conda. Fortunately, almost all Python packages can be distributed via **PyPI** system using `pip` installation.
</div>

### Via PyPI

```{r}
reticulate::conda_install("r-reticulate",
                          packages=c("google-api-python-client","oauth2client"),
                          pip = T)
```


## Makecondition

I use **makecondition** to refer to the setup you need in R in order to use Python inside RStudio as in drake plan usage. 

```{r}
library(reticulate)
use_condaenv("r-reticulate")
```

## Exercise

Try to 

  * install scipy via Conda
  
  * install [quantecon](https://quantecon.org/quantecon-py/) via PyPI
  

<span class="badge badge-primary">R</span>
<span class="badge badge-secondary">Python</span>



